Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
TurtleScript rewrite.

@@

\subsection{TurtleScript}\label{sec:turtles}
Nell's implementation leverages Web technologies, including HTML5,
WebGL, and JavaScript, with extensive use of offline caching.
Resources are named by URL, even when disconnected from the
internet.  This allows third parties to manage their own namespaces
when extending Nell, and simplifies updates to story modules and
the Nell system itself.
% if the kid's going to learn some software stack, this seem like a
% fine one to learn

As far as possible, Nell is implemented in JavaScript.  We have
developed a block-oriented view of JavaScript, which we call
TurtleScript~\cite{turtlescript}.  Combined with subsets of JavaScript
for beginners, this allows us to use a single implementation language
which scales from logo-like tasks all the way through the
implementation of the entire Nell system itself.  TurtleScript's block
view of JavaScript is isomorphic to the standard textual
representation of code.  We have begun implementation of a full
programming environment for TurtleScript which is naturally-suited to
tablet machines.

% XXX refer to TurtleScript excerpt in figure somewhere here.

Our goal is to allow the child to eventually dig as far into Nell's
implementation as their capabilities allow.  Although the operating system and
the browser itself are inaccessible from the web platform, we can
provide full access above that level.  The existence of meta-circular
interpreters for JavaScript~\cite{narcissus} implies that we can
expose the system all the way down to the programming language
implementation.  Via TurtleScript, this code is all visible in a
friendly block-based form.

>>>>

%%% XXX INTEGRATE THIS SECTION XXX
Nell is implemented in standard Web technologies, including HTML5,
WebGL, and JavaScript, with extensive use of offline caching.
Resources are named by URL, even when disconnected from the
internet.  This allows third parties to manage their own namespaces
when extending Nell, and simplifies updates to story modules and
the Nell system itself.
%As far as possible, Nell is implemented in JavaScript.  
% if the kid's going to learn some software stack, this seem like a
% fine one to learn

@@

\subsection{TurtleScript}\label{sec:turtles}

We have developed a block-oriented view of JavaScript, which we call
TurtleScript (Figure~\ref{fig:turtlescript}).  Combined with subsets of JavaScript
for learners, this allows us to use TurtleScript as the single
implementation language for Nell.  TurtleScript scales from Logo-like
pedagogical tasks up to the implementation of TurtleScript and the
Nell system itself.  TurtleScript's block view is isomorphic to
JavaScript's standard textual
representation, which preserves the code-reading skills of existing
programmers.  We have begun implementation of a
tablet programming environment for TurtleScript which uses
drag-and-drop, direct interaction, and intelligent prompting to reduce
text entry requirements.

% XXX refer to TurtleScript excerpt in figure somewhere here.
\begin{figure}
\centering
\epsfig{file=turtlescript.eps, height=1.5in}
\caption{Factorial function in TurtleScript~\cite{turtlescript}.}\label{fig:turtlescript}
\end{figure}

TurtleScript allows the child to dig as far into Nell's implementation
as their capabilities allow.  Although the operating system and the
browser implementation remain inaccessible, incorporating a
meta-circular interpreter for JavaScript (such as \cite{narcissus}) allows us
to expose the system all the way down to the programming
language implementation,
% Via TurtleScript, this code is all visible in a
% friendly block-based form.
